HTW Modeling

### 2024-03-22 Model/htw_model.qmd
update e2 and e3 model figures

pemp2 <- e2 |> filter(expMode2=="Test") |> mutate(Resp="Observed") |> 
  ggplot(aes(x=condit,y=vx, fill=vb, col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
  stat_bar+ 
  scale_color_manual(values = c("black" = "black"), guide = FALSE) +
  scale_size_manual(values = c("black" = .5), guide = FALSE) + 
  theme(legend.position="right", axis.title.x = element_blank(), plot.title = element_text(hjust=.50)) +
  labs(title="Empirical Data - Experiment 1",y="vx", x="Condition",fill="Band")

pmod2 <- e2_model$post_dat_l |> filter(!(Resp=="Observed")) |> 
  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
 summarize(vx=median(val)) |> 
 ggplot( aes(x=condit,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
  stat_bar + 
    facet_wrap(~Resp+rename_fm(Fit_Method), strip.position = "top", scales = "free_x") +
        scale_color_manual(values = c("black" = "black"), guide = "none") +
  scale_size_manual(values = c("black" = .5), guide = "none") +
    theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside",
         legend.position = "none",plot.title = element_text(hjust=.50),
         axis.title.x = element_blank(),
         plot.margin = unit(c(20,0,0,0), "pt")) + 
         labs(title="Model Predictions - Experiment 1 Data", y="vx")

(pemp2)  / pmod2 + 
  plot_layout(design = layout, heights = unit(c(4, 9), c('cm','null')))
```

e3_model <- load_e3()
post_tabs3 <- abc_tables(e2_model$post_dat,e3_model$post_dat_l)
train_tab3 <- abc_train_tables(e2_model$pd_train,e3_model$pd_train_l)

@@

>>>>

e3_model <- load_e3()
post_tabs3 <- abc_tables(e3_model$post_dat,e3_model$post_dat_l)
train_tab3 <- abc_train_tables(e3_model$pd_train,e3_model$pd_train_l)

@@

#modelsummary::modelsummary(list("e1"=e1_ee_brm_ae,"e2"=e2_ee_brm_ae,"e3"=e3_ee_brm_ae), gof_map = tribble())
```

```{r}
#| fig-height: 13
#| fig-width: 11

# pemp2 <- e2 |> filter(expMode2=="Test") |> mutate(Resp="Observed") |> 
#   ggplot(aes(x=condit,y=vx, fill=vb, col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
#   stat_bar+ 
#   scale_color_manual(values = c("black" = "black"), guide = FALSE) +
#   scale_size_manual(values = c("black" = .5), guide = FALSE) + 
#   theme(legend.position="right", axis.title.x = element_blank(), plot.title = element_text(hjust=.50)) +
#   labs(title="Empirical Data - Experiment 1",y="vx", x="Condition",fill="Band")

pmod2 <- e2_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
 summarize(vx=median(val)) |> 
 ggplot( aes(x=condit,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
  stat_bar + 
    facet_wrap(~Resp+rename_fm(Fit_Method), strip.position = "top", scales = "free_x") +
        scale_color_manual(values = c("black" = "black"), guide = "none") +
  scale_size_manual(values = c("black" = .5), guide = "none") +
    theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside",
         legend.position = "none",plot.title = element_text(hjust=.50),
         axis.title.x = element_blank(),
         plot.margin = unit(c(20,0,0,0), "pt")) + 
         labs(title="Model Predictions Experiment 2", y="vx")

pmod3 <- e3_model$post_dat_l |> filter(Fit_Method=="Test_Train") |> 
  group_by(id,condit, Fit_Method,Resp,bandType,bandOrder,x,vb) |> 
 summarize(vx=median(val)) |> 
 ggplot( aes(x=condit,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
  stat_bar + 
    facet_wrap(~bandOrder + Resp+rename_fm(Fit_Method), strip.position = "top", scales = "free_x") +
        scale_color_manual(values = c("black" = "black"), guide = "none") +
  scale_size_manual(values = c("black" = .5), guide = "none") +
    theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside",
         legend.position = "none",plot.title = element_text(hjust=.50),
         axis.title.x = element_blank(),
         plot.margin = unit(c(20,0,0,0), "pt")) + 
         labs(title="Model Predictions Experiment 3", y="vx")

pmod2 / pmod3
